### 2014-06-06 related_work.tex
updates

\paragraph{Cascaded detection}\label{cascaded-detection}
Detection cascades \cite{Viola2004,Felzenszwalb-CVPR-2010} are a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers. This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}. Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade}. While previous cascade schemes rely on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.

>>>>

\paragraph{Cascaded detection}\label{cascaded-detection}
Detection cascades \cite{Viola2004,Felzenszwalb-CVPR-2010} are a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers. This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}. Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade} as well as a boosted cascade trained on CNN features \cite{Zou-CVPR-2014}. While previous cascade schemes rely on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.
